Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging

### 2019-03-27 ms5n17-tlp-mn-180216-001.tex
most of the comments are fixed

\documentclass[preprint,5p]{elsarticle}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno}
%\linenumbers
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

that allow insertion of a removable microfluidic device into the detector have
been described~\cite{Spengler-2014,Spengler-2016,gream_2016}.

@@

In the remainder of this paper, we discuss the probe design in more detail,
and characterise its performance in terms of sensitivity and resolution.
We also demonstrate its application in microfluidic cell culture,
protein NMR spectroscopy, and micro-imaging.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Probe Design}
\label{sec:probe-design}
%Figure showing modular probe concept; example of probe base with several inserts\newline
%\begin{itemize}
%	\item Philosophy: use cheap materials and prefab Al profiles wherever possible
%	\item Hold it together with a small number of precision-machined parts
%	\item Generic probe base design that can accommodate a variety of inserts
%	\item Insert: PCB that accommodates both tuning/matching circuitry for up to two channels and the transmission line probe itself
%	\item Tuning and matching capacitors for each channel are part of the probe base
%	\item Connection using standard coaxial RF connectors (SMP)
%	\item Microfluidic chip design; outline
%	\item Design/explosion drawings
%	\item Circuit design for double resonance
%	\item Transmission line connection between tuning/matching of 1H channel and resonator (Smith chart argument)
%	\item 38 mm bore (Bruker NB) and 45 mm bore (Varian/Agilent NB)
%\end{itemize}
\begin{figure}
\centering
\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-190205-rf-device-assembly.png}
\caption{Drawings of the detector assembly and the microfluidic device (1). A: front view; B: exploded view. Spacer (4) ensures the alignment of the sample chamber with the constrictions on the PCB planes. In A, PCB plane 5 is hidden to show the orientation of 1 with respect to PCB plane 3.}
\label{fig:rf-device-assembly}
\end{figure}

%\begin{figure}
%\centering
%\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png}
%\caption{The probe with and without sleeve.}
%\label{fig:probe}
%\end{figure}
The probe assembly design is based on readily and easily available materials and parts
with minimal need for customised fabrication.
All mechanical and electronic components are readily available from commercial sources,
with the exception of a small number of precision-machined parts which are used
to hold the assembly together. These can be ordered from commercial prototyping
manufacturers or machined in-house if mechanical workshop facilities are available.

@@

The scaffold assembly is made up of two hollow aluminium tubes (11) held together with
precision machined parts at both ends (scaffold support disks (9)).
The semi-rigid cables are  threaded through these hollow aluminium tubes
to reach the detector assembly.
Auxiliary support disks (12) provide additional rigidity for the scaffold assembly.
In our case, these were laser cut from 5~mm thick PMMA sheets,
but they may also be made by conventional machining.
A tuning and matching PCB (TMPCB, 7) is held in place on the top of the probe skeleton by
the detector support rods (8), with the semi-rigid coaxial cables providing
additional support.
The TMPCB is permantly fixed to the probe base, and serves as attachment point
for the exchangeable detector assembly. It also provides
capacitors (6) for secondary tuning and matching of the detector.
The detector assembly is connected to the TMPCB through a pair of
low-loss SMP connectors (14 in \fig{fig:ProbePhoto}).
While each detector assembly is roughly
tuned and matched with fixed circuit elements soldered onto it,
the adjustable capacitors on the TMPCB are used for
fine tuning and matching
at the magnet through tuning rods (10) which reach all the way to the probe base.

The base, the scaffold assembly and the tuning and matching PCB all have a free circular
axial bore providing access from the bottom of the probe, which can be used for
temperature and environmental control and/or fluidic connections to the sample as
needed. The detector assembly is made up of two PCBs (3 and 5), a spacer between them (4). The detector used here is based on a planar transmission line geometry as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
The transmission line detector consists of a pair of copper
planes, each with a constriction at the centre.  This geometry gives rise to an
electromagnetic eigenmode with a strong anti-node of the magnetic field between
the two planes at the site of the constriction. This concentrates the rf field
and the detection sensitivity
onto the sample area.
The shape and size of the copper structures have been chosen such as to produce
an eigenfrequency of this mode around 630~MHz. The PCBs have been designed with
solder points at the back side for chip capacitors; these can be used to tune the
resonance down to the desired proton Larmor frequency (500 or 600~MHz in the present case).
Both the PCBs (3 and 5) also carry circuitry for channel separation and primary
matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs
together at the top, and forms the top end of the probe assembly.
The probe sheath (not shown in~\fig{fig:probe-explode}) is fixed to the auxiliary disk (2)
and the scaffold assembly with screws.
An exchangeable microfluidic device (1) can be inserted from the top of the detector.
Microfluidic devices can be used as passive sample holders, filled before putting them
into the probe,
or the device can be actively perfused and operated in-situ.
The microfluidic device is held in place by the spacer
between the two PCB planes coinciding the sample chamber with the constriction on the
detector.  The 45-degree edges of the device outline help with precise and reliable
alignment.
Since the detector assembly is attached to the probe base through SMP
connectors, it can easily be exchanged.
Using standard PCB processes to manufacture the detector provides great flexibility
to optimise detector performance for different applications, including different
microfluidic sample sizes, and different combinations of target nuclei.

@@

Microfluidic devices are made from inexpensive PMMA sheets by laser cutting and
thermal bonding, as described in detail elsewhere \cite{yilmaz_bonding}.
Briefly, the devices consist of a 0.5~mm thick middle layer between a  top and
bottom layer of 0.2~mm thickness each. The sample chamber and fluidic network
are cut into the middle layer. The fluidic network on the device can be designed
freely as long as the overall shape of the device is preserved, and the location
of the sample chamber is maintained. The volume of the sample chamber is 2.5~$\mu$l which can be increased or decreased according to the experimental requirments.

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png}
\caption{Microfluidic devices for different applications compatible with the current setup.
From left: Devices for perfusion of tissue slice on a chip, peristaltic pumping to induce flow,
hydrogenation on a chip, droplet generator, simple design to fill the sample chamber and,
to grow cells on the device.}
\label{fig:device}
\end{figure}

The double resnance circuit is based on the design shown in \fig{fig:circuit}.
%The size of the constriction was larger compared to~\cite{gream_2016} to allow use of larger
%sample volumes for some cases.
The transmission line detector is tuned to the desired proton
Larmor frequency by chip capacitors located at its four corners,
as well as a non-magnetic trimmer capacitor ($C_6$). Two primary
matching capacitors ($C_5$ and $C_5'$) bring the impedance into the
vicinity of 50$\Omega$. A short microstrip
with a specific impedance of 50$\Omega$
on the PCB then provides a connection to the secondary tuning and matching elements on the TMPCB ($C_1$ and $C_2$).
The lower frequency channel is connected to the detector through a high-frequency band reject ($C_7$, $L_7$).
Tuning is achieved by $L_1$ and $C_4$, which are both located on the exchangeable insert (13), in combination with
the complex admittance of the detector at the X channel frequency.
To maximise efficiency, $L_1$ should have as high a $Q$-factor as possible. We have
used commercially available flat copper coils of 5 mm diameter and 4.5 turns in the case of
\textsuperscript{15}N at 60 MHz. Tuning to \textsuperscript{13}C, either at 125 or at 150 MHz
could be achieved without $L_1$.

\begin{figure}
\centering
\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
\caption{Circuit diagram of the double resonance probe.
Proton frequency is fed in from the left (port 2) and X frequency is fed in from right (port 7).
}
\label{fig:circuit}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
%\begin{itemize}
%	\item Design process (SolidWorks, etc)
%	\item Manufacture of parts (ProtoLabs, some in-house machining)
%	\item Optimisation of resonator geometry (ref Graeme's paper)
%	\item Design and optimisation of tuning/matching circuitry (Mathematica routines)
%	\item Design of PCB using KiCAD
%	\item PCB material and manufacture
%	\item Assembly, soldering
%	\item NMR spectrometers and parameters
%	\item samples
%\end{itemize}
%The probe base platform is made up of 6 mm thick aluminium sheet [$l\times w \times h = 150 mm\times 150mm\times 75mm$]. Probe sleeve has diameter of 38 mm compatible with Bruker 500 MHz. The probe was used with a spacer on varian 600 MHz.
All the parts and the probe assembly were designed in Solidworks (Solidworks,
Dassault Syst\`{e}mes). Prefabricated profiles made from 6061-T3 aluminium
(Aluminum Warehouse, UK) were used for the mechanical structure of the probe
(base platform, scaffold tubes, sleeve). A few customised precision-machined
parts (scaffold support disks, top disk) were obtained from ProtoLabs (Telford,
UK) after providing CAD files. A small number parts were machined in-house
(detector support rods, auxiliary support disks). All  electronic components
including semi-rigid transmission lines were purchased from DigiKey Ltd. Cell
cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment
(Wendover, UK). Microfluidic devices were designed on AutoCAD. PMMA sheets were
cut to desired size and functionality (holes or channels) using a laser
engraving system  (HPC Laser L3040), and then bonded using the protocol
described in~\cite{yilmaz_bonding}.

The precise dimensions of the detector were optimised for a given sample volume
using finite element calculations in COMSOL, as described in \cite{gream_2016}.
The RF response of the probe circuit was simulated using a symbolic network
analysis code~\cite{gream-thesis} in order to estimate appropriate component
values. Final tuning was done by trial and error using an Agilent FieldFox 4 GHz
network analyser. PCB layouts were designed using KiCAD, and then sent to
beta-layout GmbH (Aarbergen, Germany) and P.W. Circuits Ltd.~(Wigston, UK) for
manufacturing. Easily and inexpensively available FR4 PCB material
(\fig{fig:ProbePhoto}(A)) proved adequate for some purposes, but limited
resolution to about 10 Hz. A high-quality Teflon-based RF PCB material (RO3035,
Rogers Corp., USA) was therefore used for optimal performance in both
sensitivity and resolution (\fig{fig:ProbePhoto}(B)). The probe skeleton was
assembled from prefabricated aluminium tubes held with the precision-machined
scaffold disks using brass screws. Semi-rigid transmission lines were then
threaded through the tubes, and the TMPCB plate was soldered on top. The
detector planes (3 and 5) and the PMMA spacer between them were assembled using
short bits of 0.5~mm magnet wire, which were soldered to the appropriate pads in
the four corners of the detector structure.

@@

@@

\begin{figure} \centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png}
\caption{ Experimental tuning and matching curves measured at 600 MHz, 500 MHz,
60 MHz (\textsuperscript{15}N frequency at 14.1 T) and 125 MHz
(\textsuperscript{13}C frequency at  and 11.7 T). Probe can be tuned to 2
frequencies at a time, above results were measured in pairs of 600 MHz with 60
MHz and 500 MHz with 125 MHz. Decoupling can be performed at all the frequencies
as the channel separation is better than 15 decibels at all frequencies.}
\label{fig:tandm} \end{figure}
Initially, FR4 PCB material was used for the
detector assembly because of its low cost and easy availability. Inhomogeneities
in the B$_0$ field due to the glass fibre rovings in FR4's composite backing can
be seen as fringes in~\fig{fig:field map} (A). B$_{0}$ field maps of the sample
chamber were constructed from 2 gradient echo (FLASH) images having echo times
($t_{e}$) of 6 and 16 ms and repetition time ($t_{r}$) of 100 ms for both FR4
and RO3035 PCB materials with the same chip~(\fig{fig:field map}). The
brightness of each pixel is proportional to the sum of the magnitude of the two
images, whereas the colour encode the phase difference between them. The full
colour range from red to blue spans phase differences from $-\pi$ to $+\pi$.

@@

\begin{figure} \centering
\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/pcb-fieldmap-colorbar.png}
\caption{B\textsubscript{0} field map of the sample chamber for FR4 (A) and
Rogers RO3035 (B) PCB material. Both the field maps were constructed from 2
gradient echo images acquired on a chip filled with 130 mM sodium acetate
dissolved in H\textsubscript{2}O through same parameters and pulse sequence.}
\label{fig:field map}
\end{figure}

The RF field at proton frequency shows excellent homogeneity, with a
810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% measured from $^1$H nutation
of the water peak in an aqueous solution of 100~mM $^{15}$N-urea at 600~MHz. The
probe generates 100~kHz nutation frequency from 100~W input power both at
600~MHz and 500~MHz, corresponding to RF field efficiency ($B_{1}/\sqrt{power}$)
of 10 kHz/$\sqrt{W}$. The detector geometry has been optimised for a sample
volume of 5~$\mu$l. It compares reasonably well to the value of 22
kHz/$\sqrt{W}$ that has been reported by Finch et al.~\cite{gream_2016} for
single-frequency detector of half this size at a Larmor frequency of 300~MHz.
For X channel, 100~W of input power produces nutation frequencies of 6 kHz for
$^{15}$N and 14 kHz for $^{13}$C. No signs of arcing were obseved at this power
level for pulses up to 1~ms duration.

%\begin{figure}
%\centering
%\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-1-Hnutation-171216-103.png}
%\caption{$^1$H nutation acquired for water peak from a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz. The 810$^{\circ}$/90$^{\circ}$ ratio is more than 90\% at 600~MHz. The 90$^{\circ}$ pulse length is below 2.5 $\mu$ sec corresponding to 100 kHz radio-frequency field for an input power of 100 W. Similar B$_{1}$ efficiency and homogeneity was observed at 500 MHz}
%\label{fig:1H-nutation}
%\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/lineshape.png}
\caption{Spectrum of 130 mM sodium acetate dissolved in water acquired in 32 scans with water presaturation. Carbon satellites can be seen in the expanded base of the acetate line. The orange curve shows a lorentzian lineshape with full width at half maximum of 3.35 Hz.}
\label{fig:lineshape}
\end{figure}

>>>>

\documentclass[preprint,5p]{elsarticle}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno,changebar}
%\linenumbers
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

that allow insertion of a removable microfluidic device into the detector have \cbstart
been described~\cite{Spengler-2014,Spengler-2016,gream_2016,swyer2019digital}. \cbend

@@

In the remainder of this paper, we discuss the probe design in more detail,
and characterise its performance in terms of sensitivity and resolution.
We also demonstrate its application in microfluidic cell culture,
protein NMR spectroscopy, and micro-imaging.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Probe Design}
\label{sec:probe-design}
%Figure showing modular probe concept; example of probe base with several inserts\newline
%\begin{itemize}
%	\item Philosophy: use cheap materials and prefab Al profiles wherever possible
%	\item Hold it together with a small number of precision-machined parts
%	\item Generic probe base design that can accommodate a variety of inserts
%	\item Insert: PCB that accommodates both tuning/matching circuitry for up to two channels and the transmission line probe itself
%	\item Tuning and matching capacitors for each channel are part of the probe base
%	\item Connection using standard coaxial RF connectors (SMP)
%	\item Microfluidic chip design; outline
%	\item Design/explosion drawings
%	\item Circuit design for double resonance
%	\item Transmission line connection between tuning/matching of 1H channel and resonator (Smith chart argument)
%	\item 38 mm bore (Bruker NB) and 45 mm bore (Varian/Agilent NB)
%\end{itemize}
\cbstart
\begin{figure}
\centering
\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-190205-rf-device-assembly.png}
\caption{Drawings of the detector assembly and the microfluidic device (1). A: front view; B: exploded view. Spacer (4) ensures the alignment of the sample chamber with the constrictions on the PCB planes. In A, PCB plane 5 is hidden to show the orientation of 1 with respect to PCB plane 3. Thickness of each of the PCB planes is 1.52 mm and the copper layers on the PCBs is 35 $\mu$m. Both the microfluidic device and the spacer are made from PMMA and have thickness of 0.9 mm and 1 mm respectively.}
\label{fig:rf-device-assembly}
\end{figure}
\cbend
%\begin{figure}
%\centering
%\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png}
%\caption{The probe with and without sleeve.}
%\label{fig:probe}
%\end{figure}
The probe assembly design is based on readily and easily available materials and parts
with minimal need for customised fabrication.
All mechanical and electronic components are readily available from commercial sources,
with the exception of a small number of precision-machined parts which are used
to hold the assembly together. These can be ordered from commercial prototyping
manufacturers or machined in-house if mechanical workshop facilities are available.

@@

The scaffold assembly is made up of two hollow aluminium tubes (11) held together with
precision machined parts at both ends (scaffold support disks (9)).\cbstart
The semi-rigid cables (RG 402) are  threaded through these hollow aluminium tubes
to reach the detector assembly.\cbend
Auxiliary support disks (12) provide additional rigidity for the scaffold assembly.
In our case, these were laser cut from 5~mm thick poly(methyl methacrylate) (PMMA) sheets,
but they may also be made by conventional machining.
A tuning and matching PCB (TMPCB, 7) is held in place on the top of the probe skeleton by
the detector support rods (8), with the semi-rigid coaxial cables providing
additional support.
The TMPCB is permanently fixed to the probe base, and serves as attachment point
for the exchangeable detector assembly. \cbstart It also provides
trimmer capacitors (6) for secondary tuning and matching of the detector.\cbend
 The detector assembly is connected to the TMPCB through a pair of
low-loss SMP connectors (14 in \fig{fig:ProbePhoto}). \cbstart SMP Connector Receptacle Male Pin is soldered on the TMPCB and SMP Connector Jack Male Pin is soldered on the PCB plane 3. The TMPCB and 3 are connected by a coaxial connector SMP plug adapter.\cbend
While each detector assembly is roughly
tuned and matched with fixed circuit elements soldered onto it,
the adjustable capacitors on the TMPCB are used for
fine tuning and matching
at the magnet through tuning rods (10) which reach all the way to the probe base.

The base, the scaffold assembly and the tuning and matching PCB all have a free circular
axial bore providing access from the bottom of the probe, which can be used for
temperature and environmental control and/or fluidic connections to the sample as
needed. The detector assembly is made up of two PCBs (3 and 5) and a spacer (4) between them. \cbstart The spacer is made from a 1 mm thick PMMA sheet.\cbend  The detector used here is based on a planar transmission line geometry as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
The transmission line detector consists of a pair of copper
planes, each with a constriction at the centre.  This geometry gives rise to an
electromagnetic eigenmode with a strong anti-node of the magnetic field between
the two planes at the site of the constriction. This concentrates the rf field
and the detection sensitivity
onto the sample area.
The shape and size of the copper structures have been chosen such as to produce
an eigenfrequency of this mode around 630~MHz. The PCBs have been designed with
solder points at the back side for chip capacitors; these can be used to tune the
resonance down to the desired proton Larmor frequency (500 or 600~MHz in the present case).
Both the PCBs (3 and 5) also carry circuitry for channel separation and primary
matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs
together at the top, and forms the top end of the probe assembly.
The probe sheath (not shown in~\fig{fig:probe-explode}) is fixed to the auxiliary disk (2)
and the scaffold assembly with screws.
An exchangeable microfluidic device (1) can be inserted from the top of the detector.
Microfluidic devices can be used as passive sample holders, filled before putting them
into the probe,
or the device can be actively perfused and operated in-situ.\cbstart The device inlet and outlet are sealed by an optical adhesive film when using the device as passive sample holder.\cbend
 The microfluidic device is held in place by the spacer
between the two PCB planes coinciding the sample chamber with the constriction on the
detector.  The 45-degree edges of the device outline help with precise and reliable
alignment.
Since the detector assembly is attached to the probe base through SMP
connectors, it can easily be exchanged.
Using standard PCB processes to manufacture the detector provides great flexibility
to optimise detector performance for different applications, including different
microfluidic sample sizes, and different combinations of target nuclei.

@@

Microfluidic devices are made from inexpensive PMMA sheets by laser cutting and
thermal bonding, as described in detail elsewhere \cite{yilmaz_bonding}.
Briefly, the devices consist of a 0.5~mm thick middle layer between a  top and
bottom layer of 0.2~mm thickness each. The sample chamber and fluidic network
are cut into the middle layer. The fluidic network on the device can be designed
freely as long as the overall shape of the device is preserved, and the location
of the sample chamber is maintained. The volume of the sample chamber is 2.5~$\mu$l which can be increased or decreased according to the experimental requirements. \cbstart \fig{fig:device} shows various microfluidic devices.\cbend
\cbstart
\begin{table}[h]
\centering
\caption{Magnetic susceptibility values of the materials used in the probe\cite{wapler-2014,schenck-1996}}
\label{tab:susceptibility}
\begin{tabular}{||p{.3\linewidth}|p{.3\linewidth}||}
\hline
Material   & $\frac{\chi/PPM}{\rho/(g cm^{-3})}$	\\
\hline
PMMA		&-7.609(5)	\\
Copper	&-9.63	\\
FR4	&-1.918(9)		\\
Aluminium	&20.7	\\
\hline
\end{tabular}
\end{table}
\cbend
\cbstart
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png}
\caption{Microfluidic devices for different applications compatible with the current setup.
From left: Devices for perfusion of tissue slice on a chip, peristaltic pumping to induce flow,
hydrogenation on a chip, droplet generator, simple design to fill the sample chamber and,
to grow cells on the device.}
\label{fig:device}
\end{figure}
\cbend

\cbstart The double resonance circuit is based on the design shown in \fig{fig:circuit}.\cbend
%The size of the constriction was larger compared to~\cite{gream_2016} to allow use of larger
%sample volumes for some cases.
 The transmission line detector is tuned to the desired proton
Larmor frequency by chip capacitors located at its four corners,
as well as a non-magnetic trimmer capacitor ($C_6$). Two primary
matching capacitors ($C_5$ and $C_5'$) bring the impedance into the
vicinity of 50$\Omega$. A short microstrip
with a specific impedance of 50$\Omega$
on the PCB then provides a connection to the secondary tuning and matching elements on the TMPCB ($C_1$ and $C_2$).
The lower frequency channel is connected to the detector through a high-frequency band reject ($C_7$, $L_7$).
Tuning is achieved by $L_1$ and $C_4$, which are both located on the exchangeable insert (13), in combination with
the complex admittance of the detector at the X channel frequency.
To maximise efficiency, $L_1$ should have as high a $Q$-factor as possible. We have
used commercially available flat copper coils of 5 mm diameter and 4.5 turns in the case of
\textsuperscript{15}N at 60 MHz. Tuning to \textsuperscript{13}C, either at 125 or at 150 MHz
could be achieved without $L_1$.
\cbstart
\begin{table}[h]
\centering
\caption{Details of the circuit elements}
\label{tab:circut}
\begin{tabular}{||p{.3\linewidth}|p{.3\linewidth}|p{.3\linewidth}||}
\hline
Circuit element   & Value	&Part Number\\
\hline
$C_1$, $C_2$ and, $C_8$		&1-23 pf	& NMAM25HV\\
$C_9$	&3-23 pf	& NMNT23-6\\
$C_3$, $C_7$	&4.3 pf		& S111TUE\\
$C_4$	&82 pf	& S111TUE\\
$C_5$, $C^{'}_{5}$	&2.4	& S111TUE\\
$L_3$, $L_7$	 &16.6 nH	& 17NGLB\\
$L_1$	&100 nH	& 4.7\\
$C_6$	&3-23 pf	& NMAJ25HV\\
$C_{20}$  & 2.4 pf		& S111TUE\\
\hline
\end{tabular}
\end{table}
\cbend
\cbstart
\begin{figure}
\centering
\includegraphics[width=.96\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
\caption{Circuit diagram of the double resonance probe.
Proton frequency is fed in from the left (port 2) and X frequency is fed in from right (port 7).
}
\label{fig:circuit}
\end{figure}
\cbend
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
%\begin{itemize}
%	\item Design process (SolidWorks, etc)
%	\item Manufacture of parts (ProtoLabs, some in-house machining)
%	\item Optimisation of resonator geometry (ref Graeme's paper)
%	\item Design and optimisation of tuning/matching circuitry (Mathematica routines)
%	\item Design of PCB using KiCAD
%	\item PCB material and manufacture
%	\item Assembly, soldering
%	\item NMR spectrometers and parameters
%	\item samples
%\end{itemize}
%The probe base platform is made up of 6 mm thick aluminium sheet [$l\times w \times h = 150 mm\times 150mm\times 75mm$]. Probe sleeve has diameter of 38 mm compatible with Bruker 500 MHz. The probe was used with a spacer on varian 600 MHz.
All the parts and the probe assembly were designed in Solidworks (Solidworks,
Dassault Syst\`{e}mes). Prefabricated profiles made from 6061-T3 aluminium
(Aluminum Warehouse, UK) were used for the mechanical structure of the probe
(base platform, scaffold tubes, sleeve). A few customised precision-machined
parts (scaffold support disks, top disk) were obtained from ProtoLabs (Telford,
UK) after providing CAD files. A small number parts were machined in-house
(detector support rods, auxiliary support disks). All electronic components
including semi-rigid transmission lines were purchased from DigiKey Ltd. Cell
cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment
(Wendover, UK). Microfluidic devices were designed on AutoCAD. PMMA sheets were
cut to desired size and functionality (holes or channels) using a laser
engraving system  (HPC Laser L3040), and then bonded using the protocol
described in~\cite{yilmaz_bonding}.

The precise dimensions of the detector were optimised for a given sample volume
using finite element calculations in COMSOL, as described in \cite{gream_2016}.
The RF response of the probe circuit was simulated using a symbolic network
analysis code~\cite{gream-thesis} in order to estimate appropriate component
values. Final tuning was done by trial and error using an Agilent FieldFox 4 GHz
network analyser. PCB layouts were designed using KiCAD, and then sent to
beta-layout GmbH (Aarbergen, Germany) and P.W. Circuits Ltd.~(Wigston, UK) for
manufacturing. Easily and inexpensively available FR4 PCB material
(\fig{fig:ProbePhoto}(A)) proved adequate for some purposes, but limited
resolution to about 10 Hz. A high-quality Teflon-based RF PCB material (RO3035,
Rogers Corp., USA) was therefore used for optimal performance in both
sensitivity and resolution (\fig{fig:ProbePhoto}(B)). The probe skeleton was
assembled from prefabricated aluminium tubes held with the precision-machined
scaffold disks using brass screws. Semi-rigid transmission lines were then
threaded through the tubes, and the TMPCB plate was soldered on top. The
detector planes (3 and 5) and the PMMA spacer between them were assembled using
short bits of 0.5~mm \cbstart diameter copper wire, \cbend which were soldered to the appropriate pads in
the four corners of the detector structure.

@@

\cbstart
\fig{fig:field map} were created through having echo times ($t_{e}$) of 6 and 16 ms and repetition time ($t_{r}$) of 100 ms. \fig{fig:1H-nutation} of the water peak in an aqueous solution of 100~mM $^{15}$N-urea. \fig{fig:lineshape} shows proton spectrum of 2.5 $\mu$l of 130 mM  sodium acetate dissolved in H$_2$O acquired at 600 MHz. The spectrum was acquired with water presaturation at 100~Hz. 32 transients were averaged with a repetition delay of 3~s. The proton spectrum of DMEM (Dulbecco
modified Eagle's medium) cell growth medium acquired with 256 scans in 20 mins
is shown in \fig{fig:media-spec}.
The left panel shows a $^{13}$C-$^{1}$H heteronuclear single
quantum correlation (HSQC) spectrum, acquired in 12 mins (32 t$_1$ increments
and 16 scans) from a 2.5 $\mu$l sample of 100 mM $^{13}$C-glucose dissolved in
water. The right panel shows a $^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400
mins (64 t$_1$ increments and 128 scans) from 2.5 $\mu$l sample of 1 mM
$^{15}$N-ubiquitin (17 $\mu$g) dissolved in 10 mM phosphate buffer at pH 7.
The image shown in \fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with $t_R=120$~ms
and $t_E=15.3$~ms. The slice thickness of  1~mm encompasses the entire thickness
of the tissue \fig{fig:tisli}(C) shows a
RARE image using the same parameters, with 8 echos acquired per scan, thus
reducing the acquisition time to 8 minutes. A spin echo image is shown in
\fig{fig:tisli}(D), acquired over 25~min. Finally, \fig{fig:tisli}(E) shows a
$B_0$ field map, which has been obtained by acquiring two separate FLASH images
with echo times $t_E=5.3$~ms and 15.3~ms, respectively.
\cbend

@@

\cbstart
\begin{figure} \centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png}
\caption{ Experimental tuning and matching curves measured at 600 MHz, 500 MHz,
60 MHz (\textsuperscript{15}N frequency at 14.1 T) and 125 MHz
(\textsuperscript{13}C frequency at 11.7 T). Probe can be tuned to 2
frequencies at a time, above results were measured in pairs of 600 MHz with 60
MHz and 500 MHz with 125 MHz. Decoupling can be performed at all the frequencies
as the channel separation is better than 15 decibels at all frequencies.}
\label{fig:tandm}
\end{figure}
\cbend
Initially, FR4 PCB material was used for the
detector assembly because of its low cost and easy availability. Inhomogeneities
in the B$_0$ field due to the glass fibre rovings in FR4's composite backing can
be seen as fringes in~\fig{fig:field map} (A). B$_{0}$ field maps of the sample
chamber were constructed from 2 gradient echo (FLASH) images for both FR4
and RO3035 PCB materials with the same chip~(\fig{fig:field map}). The
brightness of each pixel is proportional to the sum of the magnitude of the two
images, whereas the colour encode the phase difference between them. The full
colour range from red to blue spans phase differences from $-\pi$ to $+\pi$.

@@

\cbstart
\begin{figure} \centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/pcb-fieldmap-colorbar.png}
\caption{B\textsubscript{0} field map of the sample chamber for FR4 (A) and
Rogers RO3035 (B) PCB material acquired at 11.7 T. Both the field maps were constructed from 2
gradient echo images acquired on a chip filled with 130 mM sodium acetate
dissolved in H\textsubscript{2}O through same parameters and pulse sequence.}
\label{fig:field map}
\end{figure}
\cbend

The RF field at proton frequency shows excellent homogeneity, with a
810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% measured from $^1$H nutation at 600~MHz~\fig{fig:1H-nutation}. The
probe generates 100~kHz nutation frequency from 100~W input power both at
600~MHz and 500~MHz, corresponding to RF field efficiency ($B_{1}/\sqrt{power}$)
of 10 kHz/$\sqrt{W}$. The detector geometry has been optimised for a sample
volume of 5~$\mu$l. It compares reasonably well to the value of 22
kHz/$\sqrt{W}$ that has been reported by Finch et al.~\cite{gream_2016} for
single-frequency detector of half this size at a Larmor frequency of 300~MHz.
For X channel, 100~W of input power produces nutation frequencies of 6 kHz for
$^{15}$N and 14 kHz for $^{13}$C. No signs of arcing were obseved at this power
level for pulses up to 1~ms duration.

\cbstart
\begin{figure}
\centering
\includegraphics[width=.95\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-1-Hnutation-171216-103.png}
\caption{$^1$H nutation acquired for water peak from a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz. The 810$^{\circ}$/90$^{\circ}$ ratio is 92\% at 600~MHz. The 90$^{\circ}$ pulse length is below 2.5 $\mu$ sec corresponding to 100 kHz radio-frequency field for an input power of 100 W. Similar B$_{1}$ efficiency and homogeneity was observed at 500 MHz.}
\label{fig:1H-nutation}
\end{figure}
\cbend

@@

\begin{figure}
\centering
\includegraphics[width=.80\linewidth,keepaspectratio=true]{./figures/lineshape.png}
\caption{Spectrum of 130 mM sodium acetate dissolved in water acquired in 32 scans with water presaturation. Carbon satellites can be seen in the expanded base of the acetate line. The orange curve shows a lorentzian lineshape with full width at half maximum of 3.35 Hz.}
\label{fig:lineshape}
\end{figure}

\begin{figure*}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/media-180125-005-bigger-font.png}
\caption{Spectrum of culture growth media recorded in 256 scans with water presaturation. The total experimental time was 20 min for 2.5 $\mu$l sample volume.}
\label{fig:media-spec}
\end{figure*}
